Non-kissing complexes and tau-tilting \\ for gentle algebras

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
MAJ (a) et (b) firstPaperLong

Consider now an arrow~$\alpha \in Q\blossom_1$ and a non-kissing face~$F \in \NKC$ containing the straight walk passing through~$\alpha$.
Let~$F_\alpha$ be the set of walks of~$F$ containing~$\alpha$, marked at an occurrence of~$\alpha$.
Note that~$F_\alpha \ne \varnothing$ since it contains at least the straight walk passing through~$\alpha$, marked at~$\alpha$.
Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
On the other hand, we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.

>>>>

Consider now an arrow~$\alpha \in Q\blossom_1$ and a non-kissing face~$F \in \NKC$ containing the straight walk passing through~$\alpha$.
Let~$F_\alpha$ be the set of walks of~$F$ containing~$\alpha$, marked at an occurrence of~$\alpha$.
Note that~$F_\alpha \ne \varnothing$ since it contains at least the straight walk passing through~$\alpha$, marked at~$\alpha$.
Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
On the other hand, Proposition~\ref{prop: nk facets are finite}, below, shows that we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.
\begin{lemma}\label{lemma: distinguished arrows exists}
Let~$F$ be a finite face of~$\NKC$, let~$\omega$ be a walk in~$F$, and let~$\alpha$ be an arrow on~$\omega$.
Then, there is an arrow~$\beta$ oriented in the same direction as~$\alpha$ in~$\omega$ such that~$\omega$ (marked at~$\beta$) is maximal in~$F$ for~$\prec_\beta$.
\end{lemma}

\begin{proof}
If~$\omega$ is not maximal in~$F$ for~$\prec_\alpha$, consider~${\mu \eqdef \min_{\prec_\alpha} \set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}}$.
Let~$\sigma$ denote the maximal common substring of~$\omega$ and~$\mu$ containing~$\alpha$.
Since~$\omega$ and~$\mu$ are distinct, they split at an endpoint of~$\sigma$.
At this endpoint, the arrow~$\beta$ of~$\omega$ not in~$\sigma$ points in the same direction as~$\alpha$ since~$\omega \prec_\alpha \mu$.
Let~$\lambda$ be maximal in~$F$ for~$\prec_\beta$.
If~$\lambda \ne \omega$, then~$\lambda$ either kisses~$\mu$ or contradicts the minimality of~$\mu$ among the walks~$\set{\nu \in F_\alpha}{\omega \prec_\alpha \nu}$.
See \fref{fig:pure}\,(right) for an illustration.
We conclude that~$\lambda = \omega$ has a distinguished arrow~$\beta$ in the direction of~$\alpha$.
\end{proof}

\begin{proposition}\label{prop: nk facets are finite}
The faces of the non-kissing complex have finite cardinality.
\end{proposition}

\begin{proof}
By Lemma~\ref{lemma: distinguished arrows exists}, the cardinality of any finite non-kissing face is bounded by~$|Q_1\blossom|$.
Thus, any collection of~$|Q_1\blossom|+1$ walks contains a kiss and all non-kissing faces are finite.
% Let~$F$ be a non-kissing face.
% Since the quiver~$Q$ has a finite number of arrows, it is enough to prove that each~$F_\alpha$ is finite.
% Assume, by means of contradiction, that there is some~$\alpha\in Q_1$ with~$F_\alpha$ infinite.
% Call ``junction'' a marked occurrence of an arrow~$\beta$ in some~$\omega_\star, \omega'_\star\in F_\alpha$, such that~$\omega$ and~$\omega'$ coincide from their marked occurrence of~$\alpha$ up to~$\beta$ and differ after~$\beta$.
% Since~$F_\alpha$ is infinite, there is an infinite number of junctions.
% Since~$Q_1$ is finite, there are two junctions with the same underlying arrow~$\beta$ and such that either~$\alpha$ points towards both junctions or~$\alpha$ points to the direction opposite to both junctions.
% This shows that there exist three marked walks~$\nu_\star\prec_\alpha \mu_\star\prec_\alpha \lambda_\star\in F_\alpha$ such that~$\lambda, \mu$ and $\nu$ coincide from their marked occurrence of~$\alpha$ up to some marked occurrence~$\beta_1$ of~$\beta$, after which~$\lambda$ differs from~$\mu$ and~$\nu$ but~$\mu$ and~$\nu$ coincide up to some other occurrence~$\beta_2$ of~$\beta$, and then differ (see Figure~\ref{fig: nk facets are finite}).
% Let~$\sigma_1$ and~$\sigma_2$ be the longest common substrings of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
% Note that, since~$\nu$ is finite,~$\sigma_2$ cannot contain~$\beta_1$; in particular,~$\sigma_2$ is contained in~$\mu$.
% If~$\sigma$ is on top of~$\nu$, then it is at the bottom of~$\lambda$, and~$\lambda$ kisses~$\nu$, which is absurd.
% Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ and $\lambda$ constains a substring of the form~$\gamma^{-1}\sigma_1$, where~$\gamma$ is an arrow of~$Q$.
% If~$\mu$ entirely contains~$\gamma^{-1}\sigma_1$, then~$\sigma_1$ is at the top of~$\mu$.
% Hence,~$\mu$ kisses itself, which is absurd.
% Therefore,~$\gamma^{-1}\sigma_1$ is not entirely contained in~$\mu$.
\end{proof}
